% DBM data documentation

Glossary
========
1. BESF - Budget of Expenditures and Sources of Financing
2. GAA - General Appropriations Act
3. SAOB - statement of allotments, obligations & balances
4. OSEC - office of the secretary


GAA-AA: Automatic appropriation
===============================

1. DPT_CD - department code
2. DPT_DSC - department description
3. AGY_TYPE - agency type
4. OWNER_CD - owner code ??
5. OWNER_DSC - owner description
6. FPAP_CD - 
7. FPAP_DSC
8. AREA_CD
9. AREA_DSC 
10. PS - personnel/personal services
11. MOOE - maintenance & other operating expenses
12. CO - capital outlay
13. NET - 


GAA-NA: New appropriations
==============================


SAOB: Statement of allotments, obligations and balances
=======================================================
1. period
2. agency
3. record
4. record_label
5. approp
6. allot_ps
7. allot_mode
8. allot_co
9. allot_tot
10. oblig_ps
11. oblig_mode
12. oblig_co
13. oblig_tot
14. uoblig_ps
15. uoblig_mode
16. uoblig_co
17. uoblig_tot
18. obligrate

Sample Analysis
===============

```{r,echo=FALSE}
library(ggplot2)
library(plyr)
```

```{r}
gaa.2013 <- read.csv("2013-GAA.csv")[-1,]

gaa.sum <- ddply(gaa.2013, c("DPT_CD"), 
                 function(x) c(PS=sum(x$PS,na.rm=TRUE),
                               MOOE=sum(x$MOOE,na.rm=TRUE),
                               CO=sum(x$CO,na.rm=TRUE)))

summary(gaa.sum[,2:4])
```

```{r}
qplot(gaa.sum$DPT_CD, gaa.sum$PS)
```

